### 2018-12-21 index.Rmd
Update to version 0.0-4

```{r, echo = FALSE, fig = TRUE, results = 'hide', fig.width = 12, fig.height = 8}
suppressPackageStartupMessages(library("foehnix"))
# Loading observations (data.frame), convert to zoo
data("ellboegen", package = "foehnix")
data("sattelberg", package = "foehnix")
timefun    <- function(x) as.POSIXct(x,  origin = "1970-01-01", tz = "UTC")
ellboegen  <- zoo(ellboegen[,-1],  timefun(ellboegen$timestamp))
sattelberg <- zoo(sattelberg[,-1], timefun(sattelberg$timestamp))
names(sattelberg) <- paste0("crest_", names(sattelberg))
data <- merge(ellboegen, sattelberg)
data$diff_t <- data$crest_t + 10.27 - data$t
windfilter <- list(dd = c(43, 223), crest_dd = c(90, 270))
mod <- foehnix(diff_t ~ ff, data = data, windfilter = windfilter, switch = TRUE)
# Plot
tsplot(mod, start = "2010-02-10", end = "2010-02-20")
```

>>>>

```{r, echo = FALSE, fig = TRUE, results = 'hide', fig.width = 12, fig.height = 8}
suppressPackageStartupMessages(library("foehnix"))
# Loading observations (data.frame), convert to zoo
data("ellboegen", package = "foehnix")
data("sattelberg", package = "foehnix")
timefun    <- function(x) as.POSIXct(x,  origin = "1970-01-01", tz = "UTC")
ellboegen  <- zoo(ellboegen[,-1],  timefun(ellboegen$timestamp))
sattelberg <- zoo(sattelberg[,-1], timefun(sattelberg$timestamp))
names(sattelberg) <- paste0("crest_", names(sattelberg))
data <- merge(ellboegen, sattelberg)
data$diff_t <- data$crest_t + 10.27 - data$t
filter <- list(dd = c(43, 223), crest_dd = c(90, 270))
mod <- foehnix(diff_t ~ ff, data = data, filter = filter, switch = TRUE)
# Plot
tsplot(mod, start = "2010-02-10", end = "2010-02-20")
```
